Theories of deliberated choice

### 2023-06-21 simple.tex
cross mark

Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, \text{\ding{55}}, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.

>>>>

Given $\hist \in \allhist$ and $\ar_k, \ar_l \in \allargs$, let $(\hist, \ar_k, ?, ✗, …, \ar_l, ?)$ denote the set $\set{\histl \suchthat \exists \histk \suchthat \hist \subset \histk \subset \histl \suchthat \ar_k \in \histkend \land \histk \nileadsto \phi \land \ar_l \in \histlend}$.
